%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%% Ch. 8: Conclusion and Outlook  %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% ---------------------------------------
% labels: \label{[type]:finalchap:[name]}
% ---------------------------------------

% ¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨
\newcommand{\wallsep}{\ALIASwallsep}
\newcommand\hpA{\ALIAShpA}
\newcommand\hpB{\ALIAShpB}
\newcommand\hpC{\ALIAShpC}
\newcommand\hpAB{\ALIAShpAB}
\newcommand\hpCR{\ALIAShpCR}
\newcommand\hpCI{\ALIAShpCI}
\newcommand\epsA{\ALIASepsA}
\newcommand\epsB{\ALIASepsB}
\newcommand\epsC{\ALIASepsC}
% ¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨¨



% \begin{bullets}
%     \item Surface-tension tension: There is a strong dependence on $\sigma$.
%     \item what I would do if time
%     \item actual observables
%     \item concluding remarks
% \end{bullets}






% GWs, dynamics,
We propose a semi-analytical formula for gravitational waves from two-dimensional topological defects in an FLRW universe, using differential geometry and classical field theory. 
% This is obtained through differential geometry and 
To this end, we study the Nambu--Goto dynamics of planar domain walls, and solve analytically the equation of motion for domain walls \emph{during} a symmetron phase-transition in a matter-dominated universe. 
We have not found this solution in other literature. We find that the evolution of this solution, $\epsA$, scales as the initial amplitude $\varepsilon_\ast$, and is not dependent on symmetron parameters.\footnote{\comment{A truth with modifications}; see discussion in~\cref{app:walls:surface_tension:new_limits}.} The damping in the equation of motion is determined by the \emph{model} of phase transition, which in our case is the described symmetron effective potential. Model- and parameter-dependence can still be probed by gravitational waves from this phenomenon. 
% This solution is to the best of our knowledge, . 



% Simulations
We have performed a number of periodic-box simulations to test this framework. Flat domain walls separated by $\wallsep=L_\#/2$, where $L_\#$ is the periodic length on the 3-torus, are created in a matter-dominated FLRW universe at initial  scale factor $a_\ast=0.33$. Between the eight experiments in~\cref{tab:PT:sims:sim_setups} (\simnum{0}--\simnum{7}), we vary 
box side length $L_\#$ (\simnum{4}), 
number of lattice points $N_\#$ (\simnum{3},~\simnum{5}), 
initial redshift $\redshift\ped{i}$ (\simnum{4},~\simnum{7}), 
wall width $\delta\ped{w}$ (\simnum{6}),\footnote{Which is to say we vary symmetron mass scale $\mu$, or Compton wavelength $L\nped{C}$.} %
initial perturbation amplitude $\epsast$ (\simnum{0},~\simnum{2},~\simnum{5}) and 
perturbation scale $p$ (\simnum{0},~\simnum{5}).\footnote{Scale $p$ is irrelevant in simulation~\simnum{1} as $\epsast=0$.} In the following, results from simulation~\simnum{6} are discarded (see~\cref{app:misc:sim6} for details). We also exclude simulation~\simnum{0}, as the comparison is trivial.


% Wall pos.
The evolution of the wall displacement field resulting from simulations is dependent on the initial amplitude $\epsast$, 
% Full-theory simulations give meaning to the initial amplitude $\epsast$, 
% whereas the thin-wall limit does not (as long as $\epsast \ll \tau_\ast$). 
% which disagrees with the Nambu--Goto prediction.
which refutes the thin-wall prediction 
% whereas in the thin-wall limit, they are not 
(provided $\epsast \ll \tau_\ast$). 
The difference ($\Delta \epsilon=\abs*{\epsA-\epsB}$) between simulated wall position $\epsB$ and theoretical prediction $\epsA$ is maximally $(8\pm 3)\%$ of the initial amplitude $\epsast$, and the average offset is
$(16\pm 5)\%$. Between simulations~\simnum{1},~\simnum{3}--\simnum{5} and~\simnum{7}, which all obey $\epsast\ll \wallsep/5=0.1L_\#$, the corresponding measures read $\max{(\Delta\varepsilon)} \in [13\pm 2]\epsast$ and $\avg*{\Delta \varepsilon}\in [7\pm 1]\epsast$, respectively. 


% GWs
We present only qualitative comparative analyses on the subject of spin-2 perturbations. 
As such, validations of the gravitational-wave calculations are inconclusive. Toy-model simulation results show patterns in the gravitational signature that are directly connected to the nature of the wall displacement field, but the exact relations are unclear. %\rephrase{Novel quantitative analyses is required.}
The error $\Delta \varepsilon$ propagating from the difference in wall positions %$\Delta \varepsilon = \abs*{\epsA-\epsC}$ 
is significant for the gravitational-wave modes, and we therefore use the simulated wall position as input to the formula~\cref{eq:PT:gwas:mywaves_complete_formula} for the comparison.



% Stable symmetron
We know that stochastic scalar-field fluctuations can themselves source gravitational waves~\citep{kawasakiStudyGravitationalRadiation2011}, and we can isolate the defect-sourced waves by minimising this effect. We present a protocol that tweaks the symmetron initial-conditions to our advantage and gives more flexibility to choices of parameters in deterministic toy-model simulations.





% Theoretical predictions of the wall position $\varepsilon= \epsA$ are maximum 


% \hlineSep

% \comment{intro, GWs, hva vi har gjort "vi gjorde simuleringer...", amplituden har noe å si, why adjust,
% ekstra effekter}



% % \section{Concluding remarks}
%     The Nambu--Goto formulation with time-varying surface tension gives rise to an analytically solvable equation of motion for the planar-wall perturbation in the flat FLRW universe dominated by non-relativistic matter. Simulations with two walls per box length $L_\#$ show qualitatively good correspondence with the full theory. Simulations~\simnum{1}--\simnum{5} and \simnum{7} show average and maximum errors corresponding to $(8\pm 3)\%$ and $(16\pm 5)\%$ of the initial perturbation strength $\epsast$, respectively. In restricting $\epsast <\wallsep/5$ (i.e.~excluding simulation~\simnum{2}), where $\wallsep=L_\#/2$ is the distance between every wall centre, we get $(7\pm 1)\%$ and $(13\pm 2)\%$ instead. 

%     The model-dependence in the thin-wall limit comes from the time-dependent part of the surface tension, directly related to the theory of phase-transition. In the conventional picture (\cref{eq:PT:symm_dws:chi_w_quasistatic_FLRW}), symmetron \emph{parameters} are factored out and do not affect the thin-wall motion. On the other hand, strength of fifth-force oscillations depends on $a_\ast$ and $\xi_\ast$ (see $m_\ast$ in~\cref{eq:stablesym:m_ast_def}) and can in theory affect the damping term in the equation of motion for $\varepsilon$ (see~\cref{app:walls:surface_tension:new_limits}).



%     Large fluctuations in the symmetron field can be avoided by tweaking the initial conditions to our favour, as elaborated in~\cref{app:stablesym}. This is successfully tested with a homogeneous simulation (\cref{fig:results:achi:achi_no_wall}), but time limitations will have us stop there. We acknowledge that this improvement would not necessarily affect our results particularly, but it gives a flexibility to control future similar toy-model experiments. 


%     We present only non-numerical comparative analyses on the subject of spin-2 perturbations. 
%     As such, validations of the gravitational-wave calculations are inconclusive. Toy-model simulation results show patterns in the gravitational signature that are directly connected to the nature of the wall displacement field, but the exact relations are unclear. %\rephrase{Novel quantitative analyses is required.}
%     The error propagating from the difference in wall positions ($\Delta \varepsilon = \abs*{\epsA-\epsC}$) is significant for the gravitational-wave modes, and we therefore use the simulated wall position as input to the formula~\cref{eq:PT:gwas:mywaves_complete_formula} for the comparison.


    The results overall are intriguing, and show promise of future 
    % \hyperlink{sentence1}%
    {analytical estimations of gravitational waves from topological defects}, 
    % which was one of the aims of this thesis. 
    which is the main motivation for this thesis~\citep{saikawaReviewGravitationalWaves2017}. %
    The time-varying surface tension is effectively an additional damping in the equation of motion for the wall displacement field, and during a symmetron phase-transition, there exist explicit solutions to this equation for idealised universes. Completing the framework with novel comparative analyses---both qualitative and quantitative---can potentially elucidate the dependence on symmetron parameters systematically. This would open a window of dynamical ranges and parameter spaces that simulations alone cannot encompass.



    A substantial amount of work remains if we ever want to compare this to actual gravitational-wave observations. We have not investigated the particular implications for future experiments in this thesis, but other literature~\citep{ferreiraGravitationalWavesDomain2023,clementsDetectingDarkDomain2023,paulGravitationalWaveSignatures2021,nakayamaGravitationalWavesDomain2017,hiramatsuEstimationGravitationalWave2014,hiramatsuGravitationalWavesCollapsing2010} support the hypothesis that domain wall signatures can be probed and constrained. 
    % , potentially also discarded.%\comment{or non-found}. 

    % allows for explicit solutions to the new equation of motion 

    \speak{The end.}






    % \speak{Connect to intro}

    % \paragraph{Gravitational waves.} %
    % The results regarding gravitational radiation from perturbed, planar domain walls in a matter-dominated universe are inconclusive. More thorough analysis is required for \blahblah.
    % To compare 

    % They point in the right direction, but \blahblah


    % \speak{TO-DO: Maybe hard-code reference list! + Fix 2 places with \url{something.no} (month year)}


    % \section{Applications}
    %     Similar lines-of-thought should hold for phase transitions in a variety of systems, amongst others the very early universe and particle-physics scenarios. \iftime{Write more.}




\section{Summary}
    We have provided the necessary background concerning GR and topological defects. The general dynamics of topological defects is studied, and perturbative domain-wall dynamics in expanding spacetimes are explicitly solved. The analytical solution to domain-wall perturbations during a symmetron phase-transition is, to the best of our knowledge, not found in other literature. 
    This is put in context with the full symmetry-breaking field-theory, and evaluated in simulations using \asgrd{}. We perform comparative analyses of the symmetron field, wall position and gravitational waves in the thin-wall theory and in full-theory simulations. From our results, one can argue that the Nambu--Goto framework provides valuable analytical insights to domain-wall dynamics also when the surface tension is time-dependent. We have laid a solid foundation for complementary simulations with \asgrd{} using tweaked symmetron initial conditions and continued gravitational-wave analysis.




    % In this thesis we have solved analytically the equation of motion for a perturbed planar domain wall in a matter-dominated universe during a symmetron phase-transition, using the Nambu--Goto theory. This solution was put to the test in full field-theory toy-model simulations, along with an estimation of the gravitational-wave modes generated from this motion. We investigated thoroughly the ``$\epsA$ vs. $\epsC$''-anomaly in the limited number of simulation experiments presented. We have laid a solid foundation for complementary simulations with \asgrd{} using tweaked symmetron initial conditions and continued gravitational-wave analysis. From our results, one can argue that the Nambu--Goto framework provides valuable insights to domain-wall dynamics also when the surface tension is time-dependent.





    % and  \blahblah
    
    % arguments for further analyses of ($\hpB$ vs. $\hpC$).
 
    % \speak{Prototype, toy model}
    % Verificatu

    % Open questions

    \subsection{Open questions}
    \comment{Summarise open questions} 
    What it means for the gravitational waves to have any other perturbation $\epsilon= \varepsilon(\tau) \sin{(py + \varphi)}$ is unclear. A starting point for such an analysis was provided in~\cref{app:walls:SE_tensor_alt:general}. Varying symmetron parameters, or scalar-field theory as such, was the original wish, but other analyses was prioritised. 
    We have not studied the implications for biased domain walls, but one can  \blahblah 


    




\section{Implications and applications}
    Additional validations and analyses are necessary. We refer to suggestions in~\cref{sec:whatif:cont}. 
    Most urgent is possibly the need for an intuitive statistical measure of the gravitational waves. 



    Similar lines-of-thought should be applicable to flat spacetimes where phase transition is triggered at a critical temperature instead of a critical density. 
    
    
    \iftime{Write more.}



% \speak{\section*{TO DO (end)}}
% \speak{\paragraph{Referance list:} Maybe hard-code reference list! + Fix 2 places with \url{something.no} (month year)}
% \speak{\paragraph{Verb tenses:} Consider adjusting in some chapters/sections.}


